Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-19 src/tex/ms.tex
Add testing GR part

We give a concise description of what we implement
in our code here. For more extensive  derivation of heterodyned
likelihood, we refer the reader the reference \cite{Zackay:2018qdy}.

In the heterodyned likelihood framework, the two terms in eq \ref{eq:
loglikelihood} are given by
\begin{align}
    \langle d|h \rangle &\approx \sum_b A_0(b) r^*_0(h,b) + A_1(b) r^*_1(h,b), \nonumber \\
    \langle h|h \rangle &\approx \sum_b B_0(b) |r_0(h,b)|^2 + 2 B_1(b) \Re[r_0(h,b)r_1(h,b)],
\label{eq: heterodynedlikelihood}
\end{align}

@@

% Move these to discussion

This means independent chains can now jump between modes, or within a single
mode that exhibits complex geometry that cannot be handled only through the
local sampler, which greatly reduce both the burn-in time and sampling time.

@@

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and
flexible. With a differentiable waveform model, heterodyned likelihood and
normalizing flow enhanced sampler \texttt{flowMC}, we are able to estimate the
parameters of GW150914 and GW170817 in \kw{Quote speed}. Our method is general
and extensable, \kw{continue}.

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.
% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the
neural network on a large collection of waveforms and noise realization. This
means as soon as new waveforms models and noise models are available, our
algorithm can already be deployed. Furthermore, our met hod is essentially an
MCMC algorithm, which inherits the merit of convergence measures in MCMC. As we
are only using the normalizing flow as a proposal distribution, and the
normalizing flow is trained jointly with a local sampler, we do not suffer from
overfitting since our data is always approaching the target distribution, in
this sense, we do not introduce potential extra systematic error to inference
result.

@@

% Multi-modality in testing GR PE

% Access to higher dimensional problem
While standard GW analysis goes up to 17 dimensions. non-standard GW PE problems
can have more parameters, which could potentially lead to more complicate
geometry in the target posterior. For example,

@@

% Additional traits for having differentiable waveforms
There are a number of future developments we are working on. While IMRPhenomD is
a reasonable start, it lacks some qualitative features that other
state-of-the-art models have, such as precession and eccentricity \kw{cite}. It
also has higher mismatch with reference numerical relativity waveforms compared
to other waveforms. Currently, we are working on building differentiable
IMRPhenomX and NRSurrogate waveforms. Going forward, we encourage the waveform
development community to leverage autodiff environment such as Jax when
constructing new waveform models. Having a differentiable waveform model is not
only beneficial for parameter estimation, but also for other applications such
as calibrating waveforms to numerical relativity result, as detailed in
\kw{cite}.

% Precessing waveforms and higher mode.

@@

In order to perform realistic PE with our pipeline, the detector pattern o
The current code can perform parameter estimation for any combination of the
Hanford, Livingston and Virgo detectors, under the assumption of

@@

% Interplay with importance sampling

% Multi-device scaling
The current implementation take

>>>>

We give a concise description of what we implement
in our code here. For more extensive  derivation of heterodyned
likelihood, we refer the reader the reference \cite{Zackay:2018qdy}.
In the heterodyned likelihood framework, the two terms in eq \ref{eq:
loglikelihood} are given by
\begin{align}
    \langle d|h \rangle &\approx \sum_b A_0(b) r^*_0(h,b) + A_1(b) r^*_1(h,b), \nonumber \\
    \langle h|h \rangle &\approx \sum_b B_0(b) |r_0(h,b)|^2 + 2 B_1(b) \Re[r_0(h,b)r_1(h,b)],
\label{eq: heterodynedlikelihood}
\end{align}

@@

@@

% Observation of traits of flowMC
This means independent chains can now jump between modes, or within a single
mode that exhibits complex geometry that cannot be handled only through the
local sampler, which greatly reduce both the burn-in time and sampling time.

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and
flexible. With differentiable waveform models, heterodyned likelihood and
normalizing flow enhanced sampler \texttt{flowMC}, we are able to estimate the
parameters of GW150914 and GW170817 in \kw{Quote speed}. Our method is general
and extensible, \kw{continue}.

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.
% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the neural
network on a large collection of waveforms and noise realization. This means as
soon as new waveforms models and noise models are available, our algorithm can
already be deployed. Furthermore, our method is essentially an MCMC algorithm,
which inherits the merit of convergence measures in MCMC. As we are only using
the normalizing flow as a proposal distribution, and the normalizing flow is
trained jointly with a local sampler, we do not suffer from overfitting since
our training data is being generated on-the-fly and is always approaching the
target distribution. In this sense, we do not introduce potential extra
systematic error to inference result.

@@

@@

% Additional traits for having differentiable waveforms
There are a number of future developments we are working on. While IMRPhenomD is
a reasonable start, it lacks some qualitative features that other
state-of-the-art models have, such as precession, higher mode, and eccentricity \kw{cite}. It
also has higher mismatch with reference numerical relativity waveforms compared
to more recent waveform models. Currently, we are working on building differentiable
IMRPhenomPv2 and NRSurrogate waveforms. Going forward, we encourage the waveform
development community to leverage autodiff environment such as Jax when
constructing new waveform models. Having a differentiable waveform model is not
only beneficial for parameter estimation, but also for other applications such
as calibrating waveforms to numerical relativity result, as detailed in
\kw{cite}.

% Access to higher dimensional problem
While standard GW analysis goes up to 17 dimensions. non-standard GW PE problems
can have more parameters, which could potentially lead to more complicate
geometry in the target posterior that are hard to reparameterize. For example,
there are \kw{Be specific with the number} parameterized modifications to the
waveform one can introduce whn testing GR, which means there are \kw{the number}
extra parameters one would need to consider in the PE process. Worse, these
parameters often introduce non-trivial degeneracies such as local correlation
and multi-modality. Currently testing GR is limited to varying these
modifications one at a time, partially due to the bottle neck in sampler. Given
the gradient-based and normalizing flow enhanced sampler, our code shows
potential in solving this problem in full at once.

@@

In order to perform realistic PE with our pipeline, the antenna pattern of the
detector network needed to be taken into account. Our current code can perform
parameter estimation for any combination of the Hanford, Livingston and Virgo
detectors, under the assumption of short signals such that the effect of Earth's
rotation can be ignored. For next generation detector network such as the
Einstein Telescope and the Cosmic Explorer \kw{cite}, a differentiable version
of their antennat pattern is needed.

@@

% Multi-device scaling
The current implementation takes one GPU
